Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
typo

These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity with respect to convex-elicitable properties.
The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties;
a property is $d$-indentifiable if its level sets are all $d$-flats.
\citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
Thus, the elicitation complexity with respect to identifiable properties is greater than $d$.

>>>>

These bounds address an open question of~\citet{frongillo2020elicitation}, that of developing a theory of elicitation complexity with respect to convex-elicitable properties.
The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties;
a property is $d$-identifiable if its level sets are all $d$-flats.
\citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
Thus, the elicitation complexity with respect to identifiable properties is greater than $d$.
